Covariate analysis of ROSMAP Reprocessed RNASeq (with SVA)

### 2016-06-10 code/Rmd/ROSMAP_RNASeq_SVA_Reprocessed.Rmd
Minor modifications

# library(doParallel)
# library(foreach)
# 
# cl = makeCluster(14)
# registerDoParallel(cl)

@@

@@

# Store differential expression results
write.table(DE, file = 'ROSMAPDiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('ROSMAPDiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
|  *Results*                |  *SynapseID*                     |
|  -------                  |   ---------                      |
|  Covariates               |  `r COV_OBJ$properties$id`       |
|  Raw counts (log CPM)     |  `r COUNT_OBJ$properties$id`     |
|  Residual Expression      |  `r EXP_OBJ$properties$id`       |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`      |

>>>>

library(doParallel)
library(foreach)

cl = makeCluster(14)
registerDoParallel(cl)

@@

# Store SVs
write.table(SURR.VAR, file = 'ROSMAPsurrogatevar.tsv', sep = '\t', row.names=F, quote=F)
SURR_OBJ = File('ROSMAPsurrogatevar.tsv', name = 'Surrogate Variables', parentId = CODE$properties$id)
SURR_OBJ = synStore(SURR_OBJ, used = ALL_USED_IDs, activityName = activityName,
                    executed = thisFile, activityDescription = activityDescription)

@@

# Store differential expression results
write.table(DE, file = 'ROSMAPDiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('ROSMAPDiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
|  *Results*                |  *SynapseID*                     |
|  -------                  |   ---------                      |
|  Covariates               |  `r COV_OBJ$properties$id`       |
|  Raw counts (log CPM)     |  `r COUNT_OBJ$properties$id`     |
|  Surrogate variable       |  `r SURR_OBJ$properties$id`      |
|  Residual Expression      |  `r EXP_OBJ$properties$id`       |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`      |
